Quality Definitions of Qualities

### 2019-11-06 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
indicate which definitions are 'done'. Fix 4 citations to have authors to placate bibtex.

\usepackage[round]{natbib}
\usepackage{booktabs}
\usepackage{amsmath,amsthm}

@@

@@

\subsection{Installability \oo{owner}}

@@

\subsection{Correctness \oo{owner}}

@@

\subsection{Verifiability \oo{owner}}

@@

\subsection{Validatability \oo{owner}}

@@

\subsection{Reliability \oo{owner}}

@@

\subsection{Robustness \pmi{owner}}
\begin{defn}
  The degree to which a system or component can function correctly in the
  presence of invalid inputs or stressful environmental conditions
  \citep{IEEEStdGlossarySET1990}.
\end{defn}
\begin{defn}
  The quality can be further informally refined as the ability of a software to
  keep an acceptable behaviour, expressed in terms of robustness requirements, in
  spite of exceptional or unforeseen execution conditions (such as the
  unavailability of system resources, communication failures, invalid or
  stressful inputs, etc.) \citep{fernandez2005model}.
\end{defn}
\begin{defn}
  Code possesses the characteristic of robustness to the extent that it can
  continue to perform despite some violation of the assumptions in its
  specification \citep{boehm2007software}.
\end{defn}
\begin{defn} \label{RobustnessDefnSelected}
  A program is robust if it behaves "reasonably", even in circumstances that
  were not anticipated in the requirements specification - for example, when it
  encounters incorrect input data or some hardware malfunction
  \citep{ghezzi1991fundamentals}.
\end{defn}

@@

\subsection{Performance \pmi{owner}}

@@

\subsection{Usability \jc{owner}}

ISO defines usability as
\begin{quote}
The extent to which a product can be used by specified users to achieve
specified goals with effectiveness, efficiency, and satisfaction in a specified
context of use.
\end{quote}

@@

\subsection{Maintainability \pmi{owner}}

@@

\subsection{Reusability \pmi{owner}}

@@

\subsection{Portability \pmi{owner}}
\begin{defn}
The ease with which a system or component can be transferred from one hardware
or software environment to another \citep{IEEEStdGlossarySET1990}.
\end{defn}
\begin{defn}
An application is portable across a class of environments to the degree that the
effort required to transport and adapt it to a new environment in the class is
less than the effort of redevelopment \citep{mooney1990strategies}.
\end{defn}
\begin{defn} \label{PortabilityDefnSelected}
Effort required to transfer the program from one hardware and/or software system
environment to another \citep{pressman2005software}.
\end{defn}
\begin{defn}
A set of attributes that bear on the ability of software to be transferred from
one environment to another (including the organizational, hardware, of software
environment)\citep{pfleeger2006software}.
\end{defn}
\begin{defn}
Code possesses the characteristic of portability to the extent that it can be
operated easily and well on computer configurations other than its current
one. This implies that special function features, not easily available at other
facilities, are not used, that standard library functions and subroutines are
selected for universal applicability, and so on \citep{boehm2007software}.
\end{defn}
\begin{defn}
Portability refers to the ability to run a system on different hardware
platforms \citep{ghezzi1991fundamentals}.
\end{defn}
\begin{defn}
  ``The effort required to transfer a program from one hardware and/or software
  environment to another'' \citep{McCallEtAl1977}. (As summarized in
  \citet{VanVliet2000}.)
\end{defn}

@@

\subsection{Understandability \jc{owner}}

@@

\subsection{Interoperability \ad{owner}}

@@

\subsection{Visibility/Transparency \ad{owner}}

@@

\subsection{Reproducibility \wss{owner}}

@@

\subsection{Productivity \ad{owner}}

@@

\subsection{Sustainability \wss{owner}}

@@

\subsection{Completeness \ad{owner}}

@@

\subsection{Consistency \ad{owner}}

@@

\subsection{Modifiability \jc{owner}}

@@

\subsection{Traceability \jc{owner}}

@@

\subsection{Unambiguity \wss{owner}}

@@

\subsection{Verifiability \wss{owner}}

@@

\subsection{Abstract \wss{owner}}

>>>>

\usepackage{natbib}
\usepackage{booktabs}
\usepackage{amsmath,amsthm}

@@

\newcommand{\notdone}[1]{\textcolor{red}{#1}}

@@

\subsection{\notdone{Installability} \oo{owner}}

@@

\subsection{\notdone{Correctness} \oo{owner}}

@@

\subsection{\notdone{Verifiability} \oo{owner}}

@@

\subsection{\notdone{Validatability} \oo{owner}}

@@

\subsection{\notdone{Reliability} \oo{owner}}

@@

\subsection{\notdone{Robustness} \pmi{owner}}
\begin{defn}
  The degree to which a system or component can function correctly in the
  presence of invalid inputs or stressful environmental conditions
  \citep{IEEEStdGlossarySET1990}.
\end{defn}
\begin{defn}
  The quality can be further informally refined as the ability of a software to
  keep an acceptable behaviour, expressed in terms of robustness requirements, in
  spite of exceptional or unforeseen execution conditions (such as the
  unavailability of system resources, communication failures, invalid or
  stressful inputs, etc.) \citep{fernandez2005model}.
\end{defn}
\begin{defn}
  Code possesses the characteristic of robustness to the extent that it can
  continue to perform despite some violation of the assumptions in its
  specification \citep{boehm2007software}.
\end{defn}
\begin{defn} \label{RobustnessDefnSelected}
  A program is robust if it behaves "reasonably", even in circumstances that
  were not anticipated in the requirements specification - for example, when it
  encounters incorrect input data or some hardware malfunction
  \citep{ghezzi1991fundamentals}.
\end{defn}

@@

\subsection{\notdone{Performance} \pmi{owner}}

@@

\subsection{\notdone{Usability} \jc{owner}}

\begin{defn}
The extent to which a product can be used by specified users to achieve
specified goals with effectiveness, efficiency, and satisfaction in a specified
context of use.
\end{defn}
ISO defines usability as

@@

\subsection{\notdone{Maintainability} \pmi{owner}}

@@

\subsection{\notdone{Reusability} \pmi{owner}}

@@

\subsection{\notdone{Portability} \pmi{owner}}
\begin{defn}
The ease with which a system or component can be transferred from one hardware
or software environment to another \citep{IEEEStdGlossarySET1990}.
\end{defn}
\begin{defn}
An application is portable across a class of environments to the degree that the
effort required to transport and adapt it to a new environment in the class is
less than the effort of redevelopment \citep{mooney1990strategies}.
\end{defn}
\begin{defn} \label{PortabilityDefnSelected}
Effort required to transfer the program from one hardware and/or software system
environment to another \citep{pressman2005software}.
\end{defn}
\begin{defn}
A set of attributes that bear on the ability of software to be transferred from
one environment to another (including the organizational, hardware, of software
environment)\citep{pfleeger2006software}.
\end{defn}
\begin{defn}
Code possesses the characteristic of portability to the extent that it can be
operated easily and well on computer configurations other than its current
one. This implies that special function features, not easily available at other
facilities, are not used, that standard library functions and subroutines are
selected for universal applicability, and so on \citep{boehm2007software}.
\end{defn}
\begin{defn}
Portability refers to the ability to run a system on different hardware
platforms \citep{ghezzi1991fundamentals}.
\end{defn}
\begin{defn}
  ``The effort required to transfer a program from one hardware and/or software
  environment to another'' \citep{McCallEtAl1977}. (As summarized in
  \citet{VanVliet2000}.)
\end{defn}

@@

\subsection{\notdone{Understandability} \jc{owner}}

@@

\subsection{\notdone{Interoperability} \ad{owner}}

@@

\subsection{\notdone{Visibility/Transparency} \ad{owner}}

@@

\subsection{\notdone{Reproducibility} \wss{owner}}

@@

\subsection{\notdone{Productivity} \ad{owner}}

@@

\subsection{\notdone{Sustainability} \wss{owner}}

@@

\subsection{\notdone{Completeness} \ad{owner}}

@@

\subsection{\notdone{Consistency} \ad{owner}}

@@

\subsection{\notdone{Modifiability} \jc{owner}}

@@

\subsection{\notdone{Traceability} \jc{owner}}

@@

\subsection{\notdone{Unambiguity} \wss{owner}}

@@

\subsection{\notdone{Verifiability} \wss{owner}}

@@

\subsection{\notdone{Abstract} \wss{owner}}
